\documentclass[twocolumn]{article}
\usepackage[letterspace=-80]{microtype}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usepackage{standalone}
\usepackage[includehead,includefoot,margin=1cm,headheight=1cm]{geometry}
\usepackage{stix2}
\usepackage{gillius}
\tikzset{>=stealth}
\usepackage{multicol}
\usepackage{environ}
\usepackage{lettrine}
\usepackage{mathtools}
\makeatletter
\newcommand{\mylabel}[2]{#2\def\@currentlabel{#2}\label{#1}}
\makeatother

\usepackage{qrcode}
\qrset{height=1cm}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{title}{%
\fancyhead[L]{\sffamily\flushleft
\!\resizebox{!}{.05\textheight}{\input{../wormLogo/tikzLogo.tex}}\resizebox{!}{.05\textheight}{\lsstyle
    Tech\! Brief}\\
Ximera: Interactive Mathematics Education  \\[-.1cm] Resources for All\hfill
\textsl{MathFest} 2024: August 7--9\\[.1cm]
\rule{\textwidth}{.1cm}\\[.1cm]\rmfamily
Email:~{\tt ximera@math.osu.edu} \hfill Website:~{\tt
https://github.com/ximeraProject/}}

\fancyfoot[L]{\sffamily\tiny\textbf{XIMERA\quad FORM \quad 1729 \quad GIT \quad
        COMMIT \quad
        \input{../.git/refs/heads/master} \quad PREVIOUS \quad EDITION \quad IS
        \quad OBSOLETE.}
}}

\fancypagestyle{main}{%
\fancyhead[L]{\sffamily\flushleft
\resizebox{!}{.7em}{\input{../wormLogo/tikzLogo.tex}}\resizebox{!}{.7em}{\lsstyle
    Tech\! Brief}\hfill\textsl{MathFest} 2024: August 7--9\\[-.1cm]
\rule{\textwidth}{.1cm}\\[0cm]\rmfamily
Email:~{\tt ximera@math.osu.edu} \hfill Website:~{\tt
https://github.com/ximeraProject/}}

\fancyfoot[L]{\sffamily\tiny\textbf{XIMERA\quad FORM \quad 1729 \quad GIT \quad
        COMMIT \quad
        \input{../.git/refs/heads/master} \quad PREVIOUS \quad EDITION \quad IS
        \quad OBSOLETE.}}}

\usepackage[framemethod=TikZ]{mdframed}
\NewEnviron{xframe}{%
    \begin{mdframed}[roundcorner=2pt]
        \BODY%
    \end{mdframed}%
}

\begin{document}
\newgeometry{margin=1cm,headheight=3cm,includehead,includefoot}
\pagestyle{main}
\thispagestyle{title}
\pagenumbering{gobble}
\noindent
\lettrine[lines=2]{X}{imera}, pronounced ``chimera,'' is a free and
open-source platform offering tools for authoring and publishing
interactive educational content, including textbooks, assessments, and
online
courses. Currently, Ximera materials are utilized at over a dozen
institutions. \textbf{Even with the most conservative estimates, Ximera saves
    students
    over one million dollars annually}. The ultimate goal of this project is to
promote sustained student success and savings.

\begin{xframe}
    {\sffamily\bfseries Students} interact with the \textit{content} produced within
    Ximera, hence their experience is highly dependent on the \textit{quality} of this
    content. Research \ref{F21} shows that students find Ximera materials to be more readable
    than traditional course materials and perform equivalently to those using
    proprietary textbooks and online homework systems. While students typically
    encounter Ximera through their courses, many discover it via web searches and
    use the platform as independent learners. In 2023, Ximera has over one million
    unique visitors. Since Ximera materials are free, they are accessible to
    anyone, regardless of enrollment in official courses.
\end{xframe}
\begin{xframe}
    {\sffamily\bfseries Instructors} (who are not authors) can freely use
    any Ximera materials,
    \textbf{without permission}, by simply sharing the URLs of activities
    with their students. Many first time Ximera instructors start  by
    using online Ximera content as
    ungraded assignments. Visit our website for an incomplete list of
    Ximera courses that have been deployed online.
\end{xframe}
\begin{xframe}
    {\sffamily\bfseries Authors}  write and store their content on their own
    machines and GitHub repositories.
    Authors own their content and decide how to license their content. From a
    single source written in \LaTeX, Ximera generates various output: PDF
    worksheets,
    PDF textbooks, and	PDF solution manuals, and so on. Of most interest,
    Ximera can
    also create online interactive activities:
    \begin{center}
        \begin{tikzpicture}
            \node at (-1.8,.2)
            {\resizebox{.65cm}{!}{\input{document.tex}}};
            \node at (-1.8,.2) {\small PDF};
            \node at (-2,0) {\resizebox{.65cm}{!}{\input{document.tex}}};
            \node at (-2,0) {\small PDF};
            \node at (-2.2,-.2)
            {\resizebox{.65cm}{!}{\input{document.tex}}};
            \node at (-2.2,-.2) {\small PDF};
            \draw[->] (-.6,0) -- (-1.4,0);
            \draw[->] (-.6,.2) -- (-1.4,.2);
            \draw[->] (-.6,-.2) -- (-1.4,-.2);
            \node at (0,0) {\resizebox{1cm}{!}{\input{document.tex}}};
            \node at (0,0) {\LaTeX};
            \draw[->] (.6,0) -- (1.4,0);

            \node at (2,0) {\resizebox{1cm}{!}{\input{server.tex}}};
            \draw[->] (2.6,0) -- (3.4,0);
            \node at (4,0) {\resizebox{1cm}{!}{\input{computer.tex}}};
            \node at (-2,-1) {Various};
            \node at (-2,-1.4) {PDFs};
            \node at (0,-1) {Single};
            \node at (0,-1.4) {Source};
            \node at (2,-1) {Deploy};
            \node at (2,-1.4) {Server};
            \node at (4,-1) {Students};
            \node at (4,-1.4) {Engage};

        \end{tikzpicture}
    \end{center}
    The source code used to produce PDFs can also create interactive online activities when deployed to a Ximera server. Students access this content via a URL or an assignment in their LMS.
\end{xframe}

\begin{xframe}
    {\sffamily\bfseries Get involved} by contributing as an instructor, author,
    or developer. Getting started with Ximera is easy---all you need is the
    XimeraLaTeX Package, available on CTAN. For more information, visit our
    \textit{First Steps in Ximera} GitHub repository:
    \begin{center}
        \qrcode{https://go.osu.edu/xfs}\\
        \small\tt https://go.osu.edu/xfs
    \end{center}
    As a token of our appreciation, \textbf{consider applying for a Ximera
        Flash-Grant Stipend:}
    \begin{center}
        \qrcode{https://go.osu.edu/ximera-flash-grant}\\
        \small\tt https://go.osu.edu/ximera-flash-grant
    \end{center}
    Thank you for your interest in Ximera. We encourage you to contact the
    team with any questions you may have.
\end{xframe}

\begin{xframe}
    {\sffamily\bfseries Current development} is focused on two critical aspects
    of Ximera: Streamlining the deployment process and expanding LTI 1.3
    support.
    We are leveraging Docker containers for deployment and designing an
    assignment-grade database to seamlessly serve learners at institutions that
    support LTI 1.3. Additionally, we are providing alternatives for
    self-learners
    and situations where LTI 1.3 support is not available.
    \begin{center}
        \begin{tikzpicture}
            \node at (-3,1) [cloud, draw,cloud puffs=10,cloud puff arc=120,
                aspect=2, inner ysep=1em,scale=.8] {};
            \node at (-3,1) {LMS};
            \node at (-3,-1) {\resizebox{1cm}{!}{\input{computer.tex}}};
            \node at (-3,-2) {Students with LTI};
            \draw[->] (-3.1,-.4) -- (-3.1,.4);
            \draw[<-] (-2.9,-.4) -- (-2.9,.4);
            \node at (0,0) {\resizebox{1cm}{!}{\input{modulus.tex}}};
            \node at (0,-1) {Assignment};
            \node at (0,-1.4) {Database};
            \draw[->] (-2,.8) -- (-.6,.2);
            \draw[<-] (-2.1,.6) -- (-.7,0);
            \node at (3,-1) {\resizebox{1cm}{!}{\input{server.tex}}};
            \node at (3,-2) {Deploy};
            \node at (3,-2.4) {Server};
            \node at (3,1) {\resizebox{1cm}{!}{\input{computer.tex}}};
            \node at (3,2) {Self-learner};
            \draw[->] (3.1,-.4) -- (3.1,.4);
            \draw[<-] (2.9,-.4) -- (2.9,.4);
            \draw[->] (2,.8) -- (.6,.2);
            \draw[<-] (2.1,.6) -- (.7,0);
            \draw[->] (2.3,-1) -- (.6,-.4);
            \draw[<-] (2.4,-.8) -- (.7,-.2);
        \end{tikzpicture}
    \end{center}
\end{xframe}
\begin{xframe}
    {\sffamily\bfseries Future development} will focus on making Ximera
    materials fully accessible to screen readers. While Ximera documents
    currently
    offer a basic level of accessibility, there is room for
    improvement. Areas of development include enabling seamless navigation
    between activities, enhancing navigation within activities, providing
    robust
    support for images and mathematical content, and improving the
    accessibility of
    our answer-box feature.
\end{xframe}

\restoregeometry

\begin{xframe}
    {\sffamily\bfseries Talks at \textsl{MathFest} featuring Ximera}
    \begin{itemize}
        \item[{[1]}] \textbf{Lines of Sight: Activities Related to Visual
            Perspective}. A.\ Davis; Thursday, August 8th,
        10:20am--10:35am,
        Room 309/310,
        \textit{New Twists on Your Favorite Math Circle Activity Part A}.
        \item[{[2]}] \textbf{Ximera in the Classroom}. B.\ Snapp and J.\
        Fowler;
        Friday, August 9th, 3:40pm--3:55pm, Room 313, \textit{Open-Source
            Products for
            the Advancement of Math Education Research and Practice}.
    \end{itemize}
\end{xframe}

\begin{xframe}
    {\sffamily\bfseries Selected talks and papers featuring Ximera}
    \begin{itemize}
        \item[\mylabel{F21}{[3]}] J.\ Fowler et al.\ \textit{An Open-Source
            Calculus Textbook on the Ximera Platform}. In:
        PRIMUS 31.9 (2021), pp.\ 925--939. \\%url:
        \texttt{https://doi.org/10.1080/10511970.2020.1781720}
        \qrcode{https://go.osu.edu/jfx}\quad
        {\tt  https://go.osu.edu/jfx}
        \item[{[4]}] E.\ Miller et al.\ \textit{Increasing Active Learning in
            Large, Tightly Coordinated Calculus Courses}. In: Primus 31.3--5
        (2021), pp.\
        371--392.\\
        \qrcode{https://go.osu.edu/emx}
        \quad{\tt  https://go.osu.edu/emx}
        \item[{[5]}] W.\ Obbels. \textit{Ximera Interactive Math Educational
            Resources for All: From \LaTeX\ Source Code to PDF, HTML and
            Beyond}.
        Presentation at TUG 2024.\\
        \qrcode{https://go.osu.edu/wo}\quad
        {\tt  https://go.osu.edu/wo}
        \item[{[6]}]S.D.\ Ryan \& T.M.\ Nawalaniec. \textit{An OER Approach to
            Linear Algebra}. In: PRIMUS 32.6 (2022), pp.\ 721--737.\\
        \qrcode{https://go.osu.edu/rnxo}
        \quad{\tt  https://go.osu.edu/rnxo}
        \item[{[7]}] P.\ Zachlin and A.\ Davis. \textit{A New Online
            Educational Resource (OER)
            for Linear Algebra}. In: MAA Focus 43.3 (2023), pp.\ 36--38.\\
        \qrcode{https://go.osu.edu/zdx}
        \quad{\tt  https://go.osu.edu/zdx}
    \end{itemize}
\end{xframe}

\begin{xframe}
    \textbf{Funding for the Ximera Project} is provided by
    a U.S.\ Department of Education Open Textbooks Pilot Program grant in the
    amount of \$2,125,000, from 2024--2026, with no external funding. In the
    past, the Ximera Project has
    also received support from NSF Grant DUE-1245433, the Shuttleworth
    Foundation, the Ohio State University
    Department of Mathematics, and the Affordable Learning Exchange at OSU.
\end{xframe}

\begin{xframe}
    {\sffamily\bfseries Featured Ximera activities}\hfill

    \def\arraystretch{4}%  1 is the default, change whatever you need
    \begin{tabular}{rl}
        \qrcode{https://go.osu.edu/cfa}  &
        $\underset{\small\texttt{https://go.osu.edu/cfa}}{\textit{Comprehensive
        Factoring   Practice   Quiz}}$     \\
        \qrcode{https://go.osu.edu/pcr}  &
        $\underset{\small\texttt{https://go.osu.edu/pcr}}{\textit{Precalculus
                    with
        Review}} $                         \\
        \qrcode{https://go.osu.edu/mc1}  &
        $\underset{\small\texttt{https://go.osu.edu/mc1}}{\textit{Calculus 1 at
        OSU}}$                             \\
        \qrcode{https://go.osu.edu/mc2}  &
        $\underset{\small\texttt{https://go.osu.edu/mc2}}{\textit{Calculus 2 at
        OSU}}$                             \\
        \qrcode{https://go.osu.edu/mc3}  &
        $\underset{\small\texttt{https://go.osu.edu/mc3}}{\textit{Calculus 3 at
        OSU}}$                             \\
        \qrcode{https://go.osu.edu/ila}  &
        $\underset{\small\texttt{https://go.osu.edu/ila}}{\textit{Linear
                    Algebra: An Interactive Introduction}}$        \\
        \qrcode{https://go.osu.edu/kua}  &            
        $\underset{\small\texttt{https://go.osu.edu/kua}}{\substack{\textit{\normalsize Linear
                    Algebra: An Interactive Introduction}\\ \text{(KU Leuven Server)}}}$        \\
        \qrcode{https://go.osu.edu/mepr} &
        $\underset{\small\texttt{https://go.osu.edu/mepr}}{\textit{Systems:
                    Number of
        Solutions (with Parameter)}}$      \\
        \qrcode{https://go.osu.edu/met2} &
        $\underset{\small\texttt{https://go.osu.edu/met2}}{\textit{Math for
                    Elementary
                    Teachers:	 Part II}}$ \\
        \qrcode{https://go.osu.edu/qcst} &
                    $\underset{\small\texttt{https://go.osu.edu/qcst}}{\substack{\textit{\normalsize Quality Control for Introductory} \\ \textit{\normalsize Statistics and Manufacturing Courses}}}$           
    \end{tabular}
\end{xframe}

\end{document}
